---
title: "ticket solves/hour"
author: "Log"
date: "8/17/2021"
output: html_document
---
This gives us the 90th percentile for month team averages
```{r}
month_totals <- c(5.393, 6.068, 6.599, 7.104, 7.658, 6.332, 6.737, 5.575)

top_ten_team <- quantile(month_totals, .9)
median_team <- quantile(month_totals, .5)
mean_team <- mean(month_totals)
bottom_ten_team<- quantile(month_totals, .1)

(month_overall <- data.frame(top_ten_team, median_team, mean_team, bottom_ten_team))
```

It is also maybe good for us to find the 90th percentile for individuals. But how would that be done?

```{r}
#set wd

library(tidyverse)

monthly_reps <- read.csv("bigdaddyrjayyy.csv", header = TRUE)

monthly_reps_clean <- monthly_reps[,1:3]

#monthly_reps_clean <- monthly_reps %>% select(Name, Month.of.Date, formula1) %>% filter(!is.na(formula1))

top_ten_individual <- quantile(monthly_reps_clean$formula1, .9)
median_individual <- quantile(monthly_reps_clean$formula1, .5)
mean_individual <- mean(monthly_reps_clean$formula1)
bottom_ten_individual <- quantile(monthly_reps_clean$formula1, .1)

#this includes the weeks when people started and were trash

(month_overal2 <- data.frame(top_ten_individual, median_individual, mean_individual, bottom_ten_individual))
```

This is the report of our team since march

```{r}
library(tidyverse)

monthly_reps_march <- read.csv("marchnewstart.csv", header = TRUE)

monthly_reps_clean_march <- monthly_reps_march[,1:3]

#monthly_reps_clean_march <- monthly_reps_march %>% select(Name, Month.of.Date, formula1) %>% filter(!is.na(formula1))

top_ten_individual_march <- quantile(monthly_reps_clean_march$formula1, .9)
median_individual_march <- quantile(monthly_reps_clean_march$formula1, .5)
mean_individual_march <- mean(monthly_reps_clean_march$formula1)
bottom_ten_individual_march <- quantile(monthly_reps_clean_march$formula1, .1)

#this includes the weeks when people started and were trash

(month_overal3 <- data.frame(top_ten_individual_march, median_individual_march, mean_individual_march, bottom_ten_individual_march))
```



Notes:

A 6.48 ticket solve would be 56.48 tickets per day, which is a significant jump from the current expectation of 50 solves a day

Note the difference between team monthly averages and individual monthly averages

Exploration:


```{r}
monthly_reps_old <- read.csv("olddaysfadeaway.csv", header = TRUE)

monthly_reps_clean_old <- monthly_reps_old[,1:3]

#monthly_reps_clean_old <- monthly_reps_old %>% select(Name, Month.of.Date, formula1) %>% filter(!is.na(formula1))

top_ten_individual_old <- quantile(monthly_reps_clean_old$formula1, .9)
median_individual_old <- quantile(monthly_reps_clean_old$formula1, .5)
mean_individual_old <- mean(monthly_reps_clean_old$formula1)
bottom_ten_individual_old <- quantile(monthly_reps_clean_old$formula1, .1)


(month_overal4 <- data.frame(top_ten_individual_old, median_individual_old, mean_individual_old, bottom_ten_individual_old))
```


```{r}
#Let's look at a difference of means and variances

t.test(monthly_reps_clean_march$formula1, monthly_reps_clean_old$formula1, alternative = "two.sided")

var.test(monthly_reps_clean_march$formula1, monthly_reps_clean_old$formula1, alternative = "greater")
```

MX only

```{r}
#all days

monthly_reps_mx <- read.csv("mxfools1.csv", header = TRUE)

monthly_reps_clean_mx <- monthly_reps_mx[,1:3]

#monthly_reps_clean_mx <- monthly_reps_mx %>% select(Name, Month.of.Date, formula1) %>% filter(!is.na(formula1))

top_ten_individual_mx <- quantile(monthly_reps_clean_mx$formula1, .9)
median_individual_mx <- quantile(monthly_reps_clean_mx$formula1, .5)
mean_individual_mx <- mean(monthly_reps_clean_mx$formula1)
bottom_ten_individual_mx <- quantile(monthly_reps_clean_mx$formula1, .1)


(month_overal5 <- data.frame(top_ten_individual_mx, median_individual_mx, mean_individual_mx, bottom_ten_individual_mx))

#old
monthly_reps_mx2 <- read.csv("mxfools1old.csv", header = TRUE)

monthly_reps_clean_mx2 <- monthly_reps_mx2[,1:3]

monthly_reps_clean_mx2 <- monthly_reps_clean_mx2 %>% filter(!is.na(formula1))

#monthly_reps_clean_mx2 <- monthly_reps_mx2 %>% select(Name, Month.of.Date, formula1) %>% filter(!is.na(formula1))

top_ten_individual_mx2 <- quantile(monthly_reps_clean_mx2$formula1, .9)
median_individual_mx2 <- quantile(monthly_reps_clean_mx2$formula1, .5)
mean_individual_mx2 <- mean(monthly_reps_clean_mx2$formula1)
bottom_ten_individual_mx2 <- quantile(monthly_reps_clean_mx2$formula1, .1)

(month_overal7 <- data.frame(top_ten_individual_mx2, median_individual_mx2, mean_individual_mx2, bottom_ten_individual_mx2))

#recemt
monthly_reps_mx1 <- read.csv("mxfools1recent.csv", header = TRUE)

monthly_reps_clean_mx1 <- monthly_reps_mx1[,1:3]

#monthly_reps_clean_mx1 <- monthly_reps_mx1 %>% select(Name, Month.of.Date, formula1) %>% filter(!is.na(formula1))

top_ten_individual_mx1 <- quantile(monthly_reps_clean_mx1$formula1, .9)
median_individual_mx1 <- quantile(monthly_reps_clean_mx1$formula1, .5)
mean_individual_mx1 <- mean(monthly_reps_clean_mx1$formula1)
bottom_ten_individual_mx1 <- quantile(monthly_reps_clean_mx1$formula1, .1)

(month_overal6 <- data.frame(top_ten_individual_mx1, median_individual_mx1, mean_individual_mx1, bottom_ten_individual_mx1))



```


Just CX

```{r}
#all days

monthly_reps_cx <- read.csv("justcx.csv", header = TRUE)

monthly_reps_clean_cx <- monthly_reps_cx[,1:3]

#monthly_reps_clean_cx <- monthly_reps_cx %>% select(Name, Month.of.Date, formula1) %>% filter(!is.na(formula1))

top_ten_individual_cx <- quantile(monthly_reps_clean_cx$formula1, .9)
median_individual_cx <- quantile(monthly_reps_clean_cx$formula1, .5)
mean_individual_cx <- mean(monthly_reps_clean_cx$formula1)
bottom_ten_individual_cx <- quantile(monthly_reps_clean_cx$formula1, .1)


(month_overal5 <- data.frame(top_ten_individual_cx, median_individual_cx, mean_individual_cx, bottom_ten_individual_cx))

#old
monthly_reps_cx2 <- read.csv("justcxold.csv", header = TRUE)

monthly_reps_clean_cx2 <- monthly_reps_cx2[,1:3]

#monthly_reps_clean_cx2 <- monthly_reps_cx2 %>% select(Name, Month.of.Date, formula1) %>% filter(!is.na(formula1))

top_ten_individual_cx2 <- quantile(monthly_reps_clean_cx2$formula1, .9)
median_individual_cx2 <- quantile(monthly_reps_clean_cx2$formula1, .5)
mean_individual_cx2 <- mean(monthly_reps_clean_cx2$formula1)
bottom_ten_individual_cx2 <- quantile(monthly_reps_clean_cx2$formula1, .1)

(month_overal7 <- data.frame(top_ten_individual_cx2, median_individual_cx2, mean_individual_cx2, bottom_ten_individual_cx2))

#recemt
monthly_reps_cx1 <- read.csv("justcxnew.csv", header = TRUE)

monthly_reps_clean_cx1 <- monthly_reps_cx1[,1:3]

#monthly_reps_clean_cx1 <- monthly_reps_cx1 %>% select(Name, Month.of.Date, formula1) %>% filter(!is.na(formula1))

top_ten_individual_cx1 <- quantile(monthly_reps_clean_cx1$formula1, .9)
median_individual_cx1 <- quantile(monthly_reps_clean_cx1$formula1, .5)
mean_individual_cx1 <- mean(monthly_reps_clean_cx1$formula1)
bottom_ten_individual_cx1 <- quantile(monthly_reps_clean_cx1$formula1, .1)

(month_overal6 <- data.frame(top_ten_individual_cx1, median_individual_cx1, mean_individual_cx1, bottom_ten_individual_cx1))

```
I want to reorganize these dataframes to be able to manipulate the data and find monthly averages of both teams to then overlay with the tickets created per month.

```{r}
#CX team

#reformat table to have months as columns
cx_wide <- pivot_wider(monthly_reps_clean_cx, names_from = Month.of.Date, values_from = formula1)

#reorder columns to make sense chronologically
cx_wide <- cx_wide[, c(1, 9:2)]

#test na.rm on one column
mean(cx_wide$January, na.rm = TRUE)

#apply was having problems with the names column, so here we filter it out
cx_less_wide <- cx_wide[, c(2:9)]

#na.rm = true aargument ignores the na values while calculating means

(cx_avg <- apply(cx_less_wide, 2, mean, na.rm = TRUE))
  
#add in cx as team name for binding purposes
cx_df <- data.frame(lapply(cx_avg, type.convert), stringsAsFactors = FALSE)

#add name column
cx_df$Team <- "CX"

#reorder columns in df
cx_df <- cx_df[, c(9, 1:8)]


#MX team


mx_wide <- pivot_wider(monthly_reps_clean_mx, names_from = Month.of.Date, values_from = formula1)

mx_wide <- mx_wide[, c(1, 9:2)]

mx_less_wide <- mx_wide[, c(2:9)]

(mx_avg <- apply(mx_less_wide, 2, mean, na.rm = TRUE))

mx_df <- data.frame(lapply(mx_avg, type.convert), stringsAsFactors = FALSE)

mx_df$Team <- "MX"

mx_df <- mx_df[, c(9, 1:8)]


#combine the tables
all_teams <- rbind(mx_df, cx_df)


#create df of tickets created to add to the dataset



```

Explore this graphically

```{r}
#adjust dataframe for graphing
teams_long <- pivot_longer(all_teams, cols = 2:9, names_to = "month", values_to = "solves_hour")

#make months dates
month_names <- c("January", "February", "March", "April", "May", "June", "July", "August")

teams_long$month <- match(teams_long$month, month_names)

#make vector of tickets created

tickets <- data.frame(month = c("January", "February", "March", "April", "May", "June", "July", "August"),
                tickets = c(33700, 24336, 27488, 26846, 24229, 26967, 26852, 15160))

tickets$month <- match(tickets$month, month_names)

library(tidyverse)


#solves plot
solves_plot <- ggplot(data = teams_long) +  geom_path(mapping = aes(x = month, y = solves_hour, 
                                                   color = Team)) +
  xlab("Month") + ylab("Ticket Solves/Hour") + 
  ggtitle("Ticket Solves/Hour by Team")+ 
  scale_x_discrete(limits = c("January", "February", "March", "April", "May", "June", "July", "August")) +
  scale_shape_discrete(name = "Team") +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") 

#tickets plot
tickets_plot <- ggplot() +  geom_path(mapping = aes(x = tickets$month, y = tickets$tickets),
                                      show.legend = TRUE) +
  xlab("Month") + ylab("Tickets Created") + 
  ggtitle("Tickets Created by Month")+ 
  scale_x_discrete(limits = c("January", "February", "March", "April", "May", "June", "July", "August")) + 
  theme(plot.title = element_text(hjust = 0.5)) 

#stack plots
library(ggpubr)

(figure <- ggarrange(tickets_plot, solves_plot + font("x.text", size = 10),
                    ncol = 1, nrow = 2))

```


